### 2024-02-07 README.Rmd
shorten readme, change themes, let logo be autoplaced

<!-- badges: start -->

<!-- badges: end -->

@@

More details of how to operate these functions are provided in the vignette.

>>>>

@@

## Examples

In the context of the constituencies of England, Scotland and Wales, `st_bridges` will define a neighbourhood structure which includes the islands. `st_quickmap_nb` will show a representation of this on a map:

```{r, echo=FALSE}
uk_election$country <- case_when(uk_election$region == "Wales" ~ "Wales",
                                  uk_election$region == "Scotland" ~ "Scotland",
                                  TRUE ~ "England")
```

```{r, fig.width=12, fig.height=10}
nbsf <- st_bridges(df = uk_election,
                   geom_col_name = "constituency_name",
                   link_islands_k = 2)
st_quickmap_nb(nbsf,
                    pointsize=0.05, 
                    title = "st_bridges() contiguities",
                    subtitle = "islands linked to k=2 nearest constituencies")

Neighbours can be manually added or removed using `st_manual_join_nb()` and `st_manual_cut_nb()`.

```{r}
st_bridges(df = uk_election|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives") |> 
  st_quickmap_nb()
```

## Modelling & post-functions

Having set up a neighbourhood structure and embedded it as a named list or matrix within the original `sf` dataset as column `nb`, there are some functions to make it easy to quickly perform ICAR smoothing, augment the original dataframe with these predictions, and visualise them.

For example, we can use the `mgcv` package to generate a Markov Random Field ICAR smooth of poor health across the study area. This is done very quickly by using `st_bridges()` to prepare the data, putting that inside the `mgcv` GAM formulation, and then piping into the `st_augment()` and `st_quickmap_preds()` functions.

Further information and worked examples are available in this vignette.
